Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-02 Papers/ms.tex
Image of the harder data

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{substructures.pdf}
\caption{The simulated data, with substructure positions overlaid (a
Monte Carlo approximation to the posterior expectation of the empirical
measure). The density of black points in any region is proportional to the
expected number of substructures whose centers lie within that region. In this
case, there is strong evidence for a substructure close to the top-left image
(where one was actually placed).
\label{fig:substructures}}
\end{center}
\end{figure}

{\revisions
\section{``Harder'' Simulated Data}
To further test the algorithm, we created a ``harder'' simulated image, where
the lens consisted of an SIE+$\gamma$ profile plus 10 additional substructures.

}

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{substructures.pdf}
\caption{The {\revisions `easy'} simulated data, with substructure positions overlaid (a
Monte Carlo approximation to the posterior expectation of the empirical
measure). The density of black points in any region is proportional to the
expected number of substructures whose centers lie within that region. In this
case, there is strong evidence for a substructure close to the top-left image
(where one was actually placed).
\label{fig:substructures}}
\end{center}
\end{figure}

{\revisions
\section{``Harder'' Simulated Data}
To further test the algorithm, we created a ``harder'' simulated image, where
the lens consisted of an SIE+$\gamma$ profile plus 10 additional substructures.
The image is shown in Figure~\ref{fig:image2}. With the easy dataset, there
was little hope of measuring the substructure mass function parameter
$\mu_{\rm lens}$ since there was only a single substructure which would provide
little information about $\mu_{\rm lens}$ (only constraining its general
order of magnitude), even if its mass were measured perfectly.}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{image2.pdf}
\caption{{\revisions The `harder' simulated data, consisting of a more
complex source profile, and a lens with 10 substructures.}
\label{fig:image2}}
\end{center}
\end{figure}
